\sysfull

### 2018-04-13 paper/evaluation.tex
update the paging related figures; NO FULL PAGE SWAP OBSERVED

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/ramPagsSizes}
	\includegraphics[width=\columnwidth]{figures/pagefault}
	\caption{\textbf{\sys normalized runtime for various page sizes, \{32, 64, $\ldots$,1024\}\,bytes, per application (top) and respective page faults (bottom)}; X = zero page faults; red bar: half-page swap, blue bar: full page swap (replacing pages in both FRAM and SRAM).}\vspace{-0.5cm}
%\todo{change X to 0, remove the definition of X from caption}{Amjad}}
	\label{fig:page_size}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/page_exec-time}
	\includegraphics[width=\columnwidth]{figures/pagePulls}
	\caption{\textbf{\sys normalized runtime for various page sizes, \{32, 64,128,256\}\,bytes, per application (top) and respective page pulls (bottom)}).}\vspace{-0.5cm}
%\todo{change X to 0, remove the definition of X from caption}{Amjad}}
	\label{fig:page_size}
\end{figure}
